Working title: Ecological network control

### 2018-05-11 paper/manuscript.Rmd
Reference supp section on structural controllabillity

A system is said to be controllable if it is possible to steer it from an initial to an arbitrary final state within finite time [@kalman_mathematical_1963]. 
A simple dynamic system can be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example, the species' abundances), an external time-varying input *u(t)* (the control signal), and two matrices *A* and *B*, which encode information about the network structure and how species respond to external inputs, respectively. 
In classic control theory, determining wether this system is controllable or not can easily be achieved by checking that its controllability matrix $R= [ \begin{matrix}B & AB & A^{2}B & ...& A^{n-1}B\end{matrix} ]$ has full rank. 
In complex systems, however, employing this rank condition, or numerical approximations of it, is unfeasible because it is hard to fully parameterize *A* and *B* (either the weights of the links change over time or because they are difficult to measures). 
Here we use an approach based on the structural controllability theorem [@lin_structural_1974], which assumes that we are confident that the elements of *A* and *B* have either non-zero or zero values (there is an interaction or not), but that we less sure about the precise magitude of the non-zero values. 
Using this structural approach we can find out the controllability of a system under almost all non-zero parameter realisations.
In addition, a graphical interpretation of the structural controllability theorem enables us to translate the control problem into a topological one: a network is controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; see supplementary information section \@ref(S-structural-controllability) for more details).

>>>>

A system is said to be controllable if it is possible to steer it from an initial to an arbitrary final state within finite time [@kalman_mathematical_1963]. 
A simple dynamic system can be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example, the species' abundances), an external time-varying input *u(t)* (the control signal), and two matrices *A* and *B*, which encode information about the network structure and how species respond to external inputs, respectively. 
In classic control theory, determining wether this system is controllable or not can easily be achieved by checking that its controllability matrix $R= [ \begin{matrix}B & AB & A^{2}B & ...& A^{n-1}B\end{matrix} ]$ has full rank. 
In complex systems, however, employing this rank condition, or numerical approximations of it, is unfeasible because it is hard to fully parameterize *A* and *B* (either the weights of the links change over time or because they are difficult to measures). 
Here we use an approach based on the structural controllability theorem [@lin_structural_1974], which assumes that we are confident that the elements of *A* and *B* have either non-zero or zero values (there is an interaction or not), but that we less sure about the precise magitude of the non-zero values. 
Using this structural approach we can find out the controllability of a system under almost all non-zero parameter realisations.
In addition, a graphical interpretation of the structural controllability theorem enables us to translate the control problem into a topological one: a network is controllable if there are no inaccessible nodes—nodes without incoming links—or dilations—*expansions* of the network (Figure \@ref(fig:fig-example-networks)b; supplementary information section \@ref(S-structural-controllability)).
